### 2021-03-22 Figures/Graphical_Summary_Funtional_Groups.Rmd
Preparing plots 4 and 5 from models

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=13}

library(dplyr)
library(ggplot2)
library(cowplot)
##########################################
#Visualization of plant functional groups#
##########################################
setwd("~/R_Projects/Reproductive Traits")
##########################################
#Visualization of plant functional groups#
##########################################

@@

#select columns of interest
t <- d[c("Breeding_system","IMPUTED_Compatibility","Autonomous_selfing_level",
         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Flowers_per_inflorescence",
         "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
         "IMPUTED_plant_height_mean_m", "Clusters")]

@@

@@

#Plot BREEDING SYSTEM
p1 <- ggplot(breeding, aes(x = percent, y = Clusters)) +
  geom_bar(
    aes( fill = Breeding_system),alpha=0.85,
    stat = "identity", position = position_stack()) +theme_ms()+xlab("")+
  scale_fill_manual(values=c("black","orange","forestgreen"),name = "a) Breeding system")+
  theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
                                                 legend.title = element_text(face="bold"))+guides(fill=guide_legend(title.position = "top")) +ylab("Functional groups")

#######################################################################################################
#Calculate counts per group of breeding system
Compatibility <- t  %>%group_by(IMPUTED_Compatibility, Clusters) %>%summarise(counts = n()) 
Compatibility$IMPUTED_Compatibility <- as.character(Compatibility$IMPUTED_Compatibility)
Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="dioecious"] <- "Unisexual f."
Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="monoecious"] <- "Unisexual f."
Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="self_incompatible"] <- "Self inc."
Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="partially_self_compatible"] <- "Partially self com."
Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="self_compatible"] <- "Self com."

@@

Compatibility$IMPUTED_Compatibility <- factor(Compatibility$IMPUTED_Compatibility, levels=c("Unisexual f.","Self inc.", "Partially self com.",  "Self com."))

@@

Compatibility$Clusters <- factor(Compatibility$Clusters, levels=c("E","D","C", "B", "A"))
#Plot Compatibility
p2 <- ggplot(Compatibility, aes(x = percent, y = Clusters)) +
  geom_bar(
    aes( fill = IMPUTED_Compatibility),alpha=0.85,
    stat = "identity", position = position_stack()) +theme_ms()+xlab("")+
  scale_fill_manual(values=c("gray7", "orange","cyan4","deepskyblue2"),name = "b) Compatibility system")+
  theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-0,-10,-10,0),
                                                 legend.title = element_text(face="bold"))+ guides(fill=guide_legend(ncol=2,nrow=2,byrow=TRUE,title.position = "top")) +ylab("")
#######################################################################################################
#Calculate counts per group of Life form
life_form <- t  %>%group_by(life_form, Clusters) %>%summarise(counts = n()) 
life_form$life_form <- as.character(life_form$life_form)
life_form$life_form [life_form$life_form =="vine"] <- "Shrub"
life_form$life_form [life_form$life_form =="tree"] <- "Tree"
life_form$life_form [life_form$life_form =="herb"] <- "Herb"
life_form$life_form [life_form$life_form =="shrub"] <- "Shrub"

@@

p3 <- ggplot(life_form, aes(x = percent, y = Clusters)) +
  geom_bar(
    aes( fill = life_form),alpha=0.85,
    stat = "identity", position = position_stack()) +theme_ms()+xlab("")+
  scale_fill_manual(values=c("gray7", "darkorange2","forestgreen"),name = "c) Life form")+
  theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
                                                 legend.title = element_text(face="bold"))+guides(fill=guide_legend(title.position = "top"))+ylab("")
#######################################################################################################
#Calculate counts per group of Life span
lifespan <- t  %>%group_by(lifespan, Clusters) %>%summarise(counts = n()) 
#Calculate percentage of these counts
lifespan <- group_by(lifespan, Clusters) %>% mutate(percent = counts/sum(counts)*100)
#Organise levels
lifespan$lifespan <- factor(lifespan$lifespan, levels=c("Perennial","Short lived"))

@@

#Plot Compatibility
p4 <- ggplot(lifespan, aes(x = percent, y = Clusters)) +
  geom_bar(
    aes( fill = lifespan),alpha=0.85,
    stat = "identity", position = position_stack()) +theme_ms()+xlab("Percentage")+
  scale_fill_manual(values=c("sienna4","forestgreen"),name = "d) Life span")+
  theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
                                                 legend.title = element_text(face="bold"))+ guides(fill=guide_legend(ncol=2,nrow=2,byrow=TRUE,title.position = "top")) + ylab("Functional groups")
#######################################################################################################
#Calculate counts per group of Flower symmetry
Flower_symmetry <- t  %>%group_by(Flower_symmetry, Clusters) %>%summarise(counts = n()) 
#Calculate percentage of these counts
Flower_symmetry <- group_by(Flower_symmetry, Clusters) %>% mutate(percent = counts/sum(counts)*100)
Flower_symmetry$Flower_symmetry <- as.character(Flower_symmetry$Flower_symmetry)
Flower_symmetry$Flower_symmetry [Flower_symmetry$Flower_symmetry =="actinomorphic"] <- "Actinomorphic"
Flower_symmetry$Flower_symmetry [Flower_symmetry$Flower_symmetry =="zygomorphic"] <- "Zygomorphic"
#Organise levels
Flower_symmetry$Flower_symmetry <- factor(Flower_symmetry$Flower_symmetry, levels=c("Actinomorphic","Zygomorphic"))

@@

#Plot Compatibility
p5 <- ggplot(Flower_symmetry, aes(x = percent, y = Clusters)) +
  geom_bar(
    aes( fill = Flower_symmetry),alpha=0.85,
    stat = "identity", position = position_stack()) +theme_ms()+xlab("Percentage")+
  scale_fill_manual(values=c("sienna2","purple"),name = "f) Flower symmetry")+
  theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
                                                 legend.title = element_text(face="bold"))+guides(fill=guide_legend(ncol=2,nrow=2,byrow=TRUE,title.position = "top"))+ylab("")
#######################################################################################################
#Calculate counts per group of Flower shape
Flower_morphology <- t  %>%group_by(Flower_morphology, Clusters) %>%summarise(counts = n()) 
levels(Flower_morphology$Flower_morphology)
Flower_morphology$Flower_morphology <- as.character(Flower_morphology$Flower_morphology)
Flower_morphology$Flower_morphology[Flower_morphology$Flower_morphology=="Funnelform"] <- "Campanulate"
Flower_morphology$Flower_morphology[Flower_morphology$Flower_morphology=="Spike"] <- "Brush"

@@

#Plot Compatibility
p6 <- ggplot(Flower_morphology, aes(x = percent, y = Clusters)) +
  geom_bar(
    aes( fill = Flower_morphology),alpha=0.85,
    stat = "identity", position = position_stack()) +theme_ms()+xlab("Percentage")+
  scale_fill_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"),name = "e) Flower shape")+
  theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
                                                 legend.title = element_text(face="bold"))+ guides(fill=guide_legend(ncol=3,nrow=2,byrow=TRUE,title.position = "top"))+ylab("")

top <- plot_grid(p1,p2,p3,p4,p6,p5, ncol=3,nrow=2,  align = "h")

@@

top_1 <- plot_grid(title,top,ncol = 1,rel_heights = c(0.1, 1))

#Plant height
pp1 <- ggplot(t, aes(x  = log(IMPUTED_plant_height_mean_m), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
  ylab("Density") + xlab("log(Plant height)") + ggtitle("g) Plant height")  + scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))

#Flower size
pp2 <- ggplot(t, aes(x  = log(Floral_unit_width), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
  ylab("") + xlab("log(Flower size)") + ggtitle("h) Flower size") + scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))

#Ovule number
pp3 <- ggplot(t, aes(x  = log(OVULES_IMPUTED), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
  ylab("") + xlab("log(Ovule number)") +  ggtitle("i) Ovule number") +scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))

#Style length
pp4 <- ggplot(t, aes(x  = log(STYLE_IMPUTED), fill=Clusters)) +geom_density(alpha=0.3)+theme_ms()+theme(legend.position = "none")+
  ylab("Density") + xlab("log(Style length)") +  ggtitle("j) Style length") + scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))

#Flowers per plant
pp5 <- ggplot(t, aes(x  = log(Flowers_per_plant), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
  ylab("") + xlab("log(Flower number)") +  ggtitle("k) Flower number") + scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))

#Selfing
pp6 <- ggplot(t, aes(x  = Autonomous_selfing_level_fruit_set, fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
  ylab("") + xlab("Selfing") +  ggtitle("l) Selfing") + scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))

#generate panel of plots
bottom <- plot_grid(pp1,pp2,pp3,pp4,pp5,pp6, ncol=3,nrow=2,  align = "hv")
#add legend
bottom_1 <- plot_grid(bottom,legend_b,ncol = 1, rel_heights = c(1, .1))

# now add the title
title <- ggdraw() + 
  draw_label(
    "Quantitative variables",
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )
#add title
bottom_2 <- plot_grid(title,bottom_1,ncol = 1,rel_heights = c(0.1, 1))

plot_grid(top_1, bottom_2,nrow=2, align = "hv")

>>>>

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=17, fig.width=13}

library(dplyr)
library(ggplot2)
library(cowplot)

##########################################
#Visualization of plant functional groups#
##########################################
setwd("~/R_Projects/Reproductive Traits")
##########################################
#Visualization of plant functional groups#
##########################################

@@

#select columns of interest
t <- d[c("Breeding_system","IMPUTED_Compatibility","Autonomous_selfing_level",
         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Flowers_per_inflorescence",
         "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
         "IMPUTED_plant_height_mean_m","Nectar_presence_absence", "Clusters")]

@@

#Plant height
pp1 <- ggplot(t, aes(x  = log(IMPUTED_plant_height_mean_m), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
  ylab("Density") + xlab("log(Plant height)") + ggtitle("a) Plant height")  + ylab("Functional groups")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))

#Flower size
pp2 <- ggplot(t, aes(x  = log(Floral_unit_width), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
  ylab("") + xlab("log(Flower size)") + ggtitle("b) Flower size") + ylab("")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))

#Ovule number
pp3 <- ggplot(t, aes(x  = log(OVULES_IMPUTED), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
  ylab("") + xlab("log(Ovule number)") +  ggtitle("c) Ovule number") + ylab("")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))

#Style length
pp4 <- ggplot(t, aes(x  = log(STYLE_IMPUTED), fill=Clusters)) +geom_density(alpha=0.3)+theme_ms()+theme(legend.position = "none")+
  ylab("Density") + xlab("log(Style length)") +  ggtitle("d) Style length") + ylab("Functional groups")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))

#Flowers per plant
pp5 <- ggplot(t, aes(x  = log(Flowers_per_plant), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
  ylab("") + xlab("log(Flower number)") +  ggtitle("e) Flower number") + ylab("")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))

#Selfing
pp6 <- ggplot(t, aes(x  = Autonomous_selfing_level_fruit_set, fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
  ylab("") + xlab("Selfing") +  ggtitle("f) Selfing") + ylab("")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))

#generate panel of plots
top <- plot_grid(pp1,pp2,pp3,pp4,pp5,pp6, ncol=3,nrow=2,  align = "hv")
#add legend
top_1 <- plot_grid(top,legend_b,ncol = 1, rel_heights = c(1, .1))

# now add the title
title <- ggdraw() + 
  draw_label(
    "Quantitative variables",
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )
#add title
top_2 <- plot_grid(title,top_1,ncol = 1,rel_heights = c(0.1, 1))

@@

#Plot BREEDING SYSTEM
p1 <- ggplot(breeding, aes(x = percent, y = Clusters)) +
  geom_bar(
    aes( fill = Breeding_system),alpha=0.85,
    stat = "identity", position = position_stack()) +theme_ms()+xlab("")+
  scale_fill_manual(values=c("black","orange","forestgreen"),name = "g) Breeding system")+
  theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
  legend.title = element_text(face="bold"))+guides(fill=guide_legend(title.position = "top",reverse = TRUE)) +ylab("Functional groups")

#######################################################################################################
#Calculate counts per group of breeding system
Compatibility <- t  %>%group_by(IMPUTED_Compatibility, Clusters) %>%summarise(counts = n()) 
Compatibility$IMPUTED_Compatibility <- as.character(Compatibility$IMPUTED_Compatibility)
Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="dioecious"] <- "Unisexual flowers"
Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="monoecious"] <- "Unisexual flowers"
Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="self_incompatible"] <- "Self incompatible"
Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="partially_self_compatible"] <- "Partially self compatible"
Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="self_compatible"] <- "Self compatible"

@@

Compatibility$IMPUTED_Compatibility <- factor(Compatibility$IMPUTED_Compatibility, levels=c("Unisexual flowers","Self incompatible", "Partially self compatible",  "Self compatible"))

@@

Compatibility$Clusters <- factor(Compatibility$Clusters, levels=c("E","D","C", "B", "A"))
#Plot Compatibility
p2 <- ggplot(Compatibility, aes(x = percent, y = Clusters)) +
  geom_bar(
    aes( fill = IMPUTED_Compatibility),alpha=0.85,
    stat = "identity", position = position_stack()) +theme_ms()+xlab("")+
  scale_fill_manual(values=c("gray7", "orange","cyan4","deepskyblue2"),name = "h) Compatibility system")+
  theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-0,-10,-10,0),
  legend.title = element_text(face="bold"))+ guides(fill=guide_legend(ncol=2,nrow=2,byrow=TRUE,title.position = "top",reverse = TRUE)) +ylab("")
#######################################################################################################
#Calculate counts per group of Life form
life_form <- t  %>%group_by(life_form, Clusters) %>%summarise(counts = n()) 
life_form$life_form <- as.character(life_form$life_form)
life_form$life_form [life_form$life_form =="vine"] <- "Shrub"
life_form$life_form [life_form$life_form =="tree"] <- "Tree"
life_form$life_form [life_form$life_form =="herb"] <- "Herb"
life_form$life_form [life_form$life_form =="shrub"] <- "Shrub"

@@

p3 <- ggplot(life_form, aes(x = percent, y = Clusters)) +
  geom_bar(
    aes( fill = life_form),alpha=0.85,
    stat = "identity", position = position_stack()) +theme_ms()+xlab("")+
  scale_fill_manual(values=c("gray7", "darkorange2","forestgreen"),name = "i) Life form")+
  theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
                                                 legend.title = element_text(face="bold"))+guides(fill=guide_legend(title.position = "top",reverse = TRUE))+ylab("")
#######################################################################################################
#Calculate counts per group of Life span
lifespan <- t  %>%group_by(lifespan, Clusters) %>%summarise(counts = n()) 
#Calculate percentage of these counts
lifespan <- group_by(lifespan, Clusters) %>% mutate(percent = counts/sum(counts)*100)
#Organise levels
lifespan$lifespan <- factor(lifespan$lifespan, levels=c("Perennial","Short lived"))

@@

#Plot Compatibility
p4 <- ggplot(lifespan, aes(x = percent, y = Clusters)) +
  geom_bar(
    aes( fill = lifespan),alpha=0.85,
    stat = "identity", position = position_stack()) +theme_ms()+xlab("Percentage")+
  scale_fill_manual(values=c("sienna4","forestgreen"),name = "j) Life span")+
  theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
                                                 legend.title = element_text(face="bold"))+ guides(fill=guide_legend(ncol=2,nrow=2,byrow=TRUE,title.position = "top",reverse = TRUE)) + ylab("Functional groups")
#######################################################################################################
#Calculate counts per group of Flower symmetry
Flower_symmetry <- t  %>%group_by(Flower_symmetry, Clusters) %>%summarise(counts = n()) 
#Calculate percentage of these counts
Flower_symmetry <- group_by(Flower_symmetry, Clusters) %>% mutate(percent = counts/sum(counts)*100)
Flower_symmetry$Flower_symmetry <- as.character(Flower_symmetry$Flower_symmetry)
Flower_symmetry$Flower_symmetry [Flower_symmetry$Flower_symmetry =="actinomorphic"] <- "Actinomorphic"
Flower_symmetry$Flower_symmetry [Flower_symmetry$Flower_symmetry =="zygomorphic"] <- "Zygomorphic"
#Organise levels
Flower_symmetry$Flower_symmetry <- factor(Flower_symmetry$Flower_symmetry, levels=c("Actinomorphic","Zygomorphic"))

@@

#Plot Compatibility
p5 <- ggplot(Flower_symmetry, aes(x = percent, y = Clusters)) +
  geom_bar(
    aes( fill = Flower_symmetry),alpha=0.85,
    stat = "identity", position = position_stack()) +theme_ms()+xlab("Percentage")+
  scale_fill_manual(values=c("sienna2","purple"),name = "l) Flower symmetry")+
  theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
  legend.title = element_text(face="bold"))+guides(fill=guide_legend(ncol=2,nrow=2,byrow=TRUE,title.position = "top",reverse = TRUE))+ylab("")
#######################################################################################################
#Calculate counts per group of Flower shape
Flower_morphology <- t  %>%group_by(Flower_morphology, Clusters) %>%summarise(counts = n()) 
levels(Flower_morphology$Flower_morphology)
Flower_morphology$Flower_morphology <- as.character(Flower_morphology$Flower_morphology)
Flower_morphology$Flower_morphology[Flower_morphology$Flower_morphology=="Funnelform"] <- "Campanulate"
Flower_morphology$Flower_morphology[Flower_morphology$Flower_morphology=="Spike"] <- "Brush"

@@

#Plot Compatibility
p6 <- ggplot(Flower_morphology, aes(x = percent, y = Clusters)) +
  geom_bar(
    aes( fill = Flower_morphology),alpha=0.85,
    stat = "identity", position = position_stack()) +theme_ms()+xlab("Percentage")+
  scale_fill_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"),name = "k) Flower shape")+
  theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
  legend.title = element_text(face="bold"))+ guides(fill=guide_legend(ncol=3,nrow=2,byrow=TRUE,title.position = "top",reverse = TRUE))+ylab("")

#######################################################################################################
#Plot Nectar
#Calculate counts per group of Flower shape
Nectar_presence_absence <- t  %>% group_by(Nectar_presence_absence, Clusters) %>%summarise(counts = n()) 
levels(Nectar_presence_absence$Nectar_presence_absence)
Nectar_presence_absence$Nectar_presence_absence <- as.character(Nectar_presence_absence$Nectar_presence_absence)
Nectar_presence_absence$Nectar_presence_absence[Nectar_presence_absence$Nectar_presence_absence=="yes"] <- "Yes"
Nectar_presence_absence$Nectar_presence_absence[Nectar_presence_absence$Nectar_presence_absence=="no"] <- "No"

Nectar_presence_absence$Nectar_presence_absence <- factor(Nectar_presence_absence$Nectar_presence_absence, levels=c("No","Yes"))

#Calculate percentage of these counts
Nectar_presence_absence <- group_by(Nectar_presence_absence, Clusters) %>% mutate(percent = counts/sum(counts)*100)

Nectar_presence_absence$Clusters <- as.character(Nectar_presence_absence$Clusters)

Nectar_presence_absence$Clusters[Nectar_presence_absence$Clusters=="1"] <- "A"
Nectar_presence_absence$Clusters[Nectar_presence_absence$Clusters=="2"] <- "B"
Nectar_presence_absence$Clusters[Nectar_presence_absence$Clusters=="3"] <- "C"
Nectar_presence_absence$Clusters[Nectar_presence_absence$Clusters=="4"] <- "D"
Nectar_presence_absence$Clusters[Nectar_presence_absence$Clusters=="5"] <- "E"

Nectar_presence_absence$Clusters <- factor(Nectar_presence_absence$Clusters, levels=c("E","D","C", "B", "A"))

p7 <- ggplot(Nectar_presence_absence, aes(x = percent, y = Clusters)) +
  geom_bar(
    aes( fill = Nectar_presence_absence),alpha=0.85,
    stat = "identity", position = position_stack()) +theme_ms()+xlab("Percentage")+
  scale_fill_manual(values=c("black","darkorange"),name = "m) Nectar production")+
  theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
  legend.title = element_text(face="bold"))+ guides(fill=guide_legend(ncol=3,nrow=2,byrow=TRUE,title.position = "top",reverse = TRUE))+ylab("")

bottom <- plot_grid(p1,p2,p3,p4,p6,p5,NULL,p7,NULL, ncol=3,nrow=3,  align = "h")

@@

bottom_1 <- plot_grid(title,bottom,ncol = 1,rel_heights = c(0.1, 1))

plot_grid(top_2, bottom_1,nrow=2, align = "hv")
